---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidydrfrost

<!-- badges: start -->
<!-- badges: end -->

tidydrfrost allows you to automate and complete [Dr Frost Maths](https://www.drfrostmaths.com/) tasks using R. This allows points and mastery to be quickly and easily gained.

## Installation

You can install the development version of tidydrfrost from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ashbythorpe/tidydrfrost")
```

## Using the package

Interacting with [Dr Frost Maths](https://www.drfrostmaths.com/) is very simple.

```{r setup}
library(tidydrfrost)
```

The package revolves around a single function:

```{r, eval = FALSE}
perform_tasks()
```

This function will perform all tasks that have been implemented. Each task awards a certain number of points. Alternatively, you can specify the tasks to complete:

```{r, eval = FALSE}
perform_tasks(c("addition_subtraction", "multiplication"))
```

For a more controlled approach to specifying tasks, use the `dr_frost_tasks()` function.

```{r, eval = FALSE}
tasks <- dr_frost_tasks(exclude = "division")
perform_tasks(tasks)
```

Currently the following tasks have been implemented:
```{r}
dr_frost_tasks()
```

## Logging in
For the `perform_tasks()` function to work, you need to specify a Dr Frost Maths account.

```{r, eval = FALSE}
perform_tasks(
  email = "YOUR-EMAIL",
  password = "YOUR-PASSWORD"
)
```

If you don't want to specify this each time you use the function, use the `dr_frost_account()` function. This uses [keyring](https://r-lib.github.io/keyring) as its backend, allowing your credentials to be securely stored between sessions.

```{r, eval = FALSE}
dr_frost_account("YOUR-EMAIL")
```

Once you have stored your account, the `perform_tasks()` function can be called without having to specify an email or password.
